Rising from the Ashes II.: something something

### 2024-09-02 paper/ms.tex
Add disc section on cause of bimodal

\section{Discussion}\label{sec:disc}
In Figure~\ref{fig:fig1}, we compared the abundance plane between the Milky Way and our subhalo of interest. The result is quite simple, and indicates a fairly straightforward conclusion: multimodality is enhanced when \alphaFe{} more strongly declines with time.

>>>>

\section{Discussion}\label{sec:disc}
In Figure~\ref{fig:fig1}, we compared the abundance plane between the Milky Way and our SOI before and after the $\alpha$-enhancement. It is visibly obvious that the TNG SOI is unimodal before the $\alpha$-enhancement and bimodal afterwards (ignoring the minor mode at high-\MgFe{}). Here, we briefly discuss two main points: (1) assuming the $\alpha$-enhancement is justified, what leads to the bimodality in the SOI?, and (2) what justifies the $\alpha$-enhancement? We then briefly extend our comparison to the Milky Way data.

\subsection{Cause of Bimodality}\label{ssec:bim_cause}
An extensive analysis of our SOI is beyond the scope of this project, but here we argue that the evidence is consistent with the scenario presented in \citet{2024arXiv240707985B}. They presented an idealized simulation resembling the merger between the Milky Way and GSE. They varied the orbital parameters slightly in a grid of 27 simulations and found that simulations which had a brief quiescent period as a result of the merger led to a bimodal abundance distribution. They argued that AGN activity was responsible for this brief quenching.

Once the $\alpha$-enhancement post-processing has been done, the SoI that we have studied in this work is consistent with this scenario. The vertical dashed line in Figures~\ref{fig:alpha} and \ref{fig:history} denotes the transition between the high- and low-$\alpha$ sequences. We place it at an age of $10.75\,\Gyr$ or a formation time of $\sim3\,\Gyr$. The upper right panel of Figure~\ref{fig:alpha} shows 2D histograms of \MgFe{} vs star particle age in fixed bins of \FeH{} (each color is a different \FeH{} bin, and an offset is given to \MgFe{} to avoid overlap). Stars which formed before the dashed line had a steep decline of \MgFe{} with time, while the relation in star particles formed after the dashed line is much more flat. At the line, we see a gap in the $\FeH=-0.5$ and $-0.25$ bins.

The gap in each \FeH{} bin of Figure~\ref{fig:alpha} is contemperaneous with a minimum in the global SFR. We can see in the upper panel of Figure~\ref{fig:history} that this dashed line lies almost exactly at the point of a local minimum in the SFH. This minimum, which is $\sim10\,\Msunyr$, is 6--7$\times$ smaller than the maxima before and after it.\footnote{A reasonable argument can be made that $10\,\Msunyr$ is hardly quiescent. However, for our purposes, it only matters that the SFR at the minimum is small relative to the SFR close in time before and after. And besides, this SFH is computed using the formation times of all star particles at $z=0$, which is likely contaminated by later mergers.}

During this period of suppressed SF, we argue that the relative lack of enrichment of Type~II SNe which leads to a lower rate of Mg production. This leads to a rapid reduction in \MgFe{}. This, combined with a lack of SF in the first place, leads to a scarcity of star particles in the region intermediate between the high- and low-$\alpha$ sequences. A more in-depth explanation is given in Section~4.1 in \citet{2024arXiv240707985B}.

In the fiducial TNG distribution shown in the upper middle panel of Figure~\ref{fig:alpha}, the same general behavior with respect to the dashed line is present. However, because the \MgFe{} decline before the dashed line is not as strong, star particles which formed before and after the dashed line overlap in the \MgFe{} distribution shown in Figure~\ref{fig:fig1}.

It is also worth noting that in both the fiducial and $\alpha$-enhanced SOI, there is a sort of rebound effect in \MgFe{}. The star particles which form directly after the dashed line have a slightly lower \MgFe{} than stars which form after. This was seen in Figure~9 of \citet{2024arXiv240707985B}. In that work, it was argued that this occurs because during the period of suppressed star formation the \alphaFe{} of star forming gas plummets since there is no contribution from Type~II SNe. Later, the \alphaFe{} will recover when the SFR also recovers, but there is a brief window when old, low-$\alpha$ stars can form.
